VM-Centric Snapshot Deduplication for Converged Cloud Architectures

### 2014-07-19 snapshot_system/paper_eval.tex
re

\section{Evaluation}
\label{sect:evaluation}
We have implemented and evaluated a prototype of our VC scheme on a Linux cluster of machines with
8-core 3.1Ghz AMD FX-8120 and 16 GB RAM. 
Our implementation is based on the Alibaba cloud platform~\cite{Aliyun,WeiZhangIEEE}
and the underlying DFS uses  QFS with default replication degree 3 while the PDS replication degree is 6.
Our evaluation objective is to
study the benefit in fault tolerance and   deduplication efficiency of VC,  
and assess its backup throughput and  resource usage.

We will compare VC with a VO approach  using stateless routing with binning (SRB) 
based on~\cite{Dong2011,extreme_binning09}.
SRB executes distributed deduplication by routing data chunks to cluster machines~\cite{Dong2011}
using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to
a machine, the chunk is compared with the fingerprint index within this machine locally based 
on~\cite{extreme_binning09}.

@@

Table~\ref{tab:efficiency-comparison} shows the deduplication efficiency and per-machine memory usage for SRB and VC with different 
settings.
% <<<<<<< HEAD
% Our deduplication efficiency is defined as the percent of duplicate chunks
% which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
% The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
% is defined in Table~\ref{tab:symbol}. 
% =======
Deduplication efficiency is defined as the percent of duplicate chunks which are removed
compared to a perfect scheme which detects and removes  all duplicates. 
% so only global perfect deduplication can have 100\% efficiency.
% We also compare several PDS sizes chosen for VC.
%(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
Notice $\sigma$ is the percentage of unique chunks selected in PDS.
With $\sigma =2\%$, Column 3 shows its 
%memory usage for PDS index lookup per machine is about 100MB per machine and  the 
deduplication efficiency can 
reach over 96\%. 
%When $\sigma=4\%$, Column 4 shows that the deduplication efficiency can reach 96.6\% while 
%more index space is allocated  per machine for  PDS fingerprint lookup.
The loss of efficiency in VC is caused by the restriction of the physical memory available
in the cluster for fast in-memory PDS index lookup. 
Memory usage per machine is low because each machine only hosts $1/p$  of  index for PDS 
plus some buffer space where $p$ is the number of physical machines. 
%In the extreme case if we put all the fingerprint into PDS 
%index ($\sigma=100\%$) then VC will have 100\% efficiency.
SRB in Column 5 can deliver up to 97.86\% deduplication efficiency, which is slightly better than VC.
Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
with a slight reduction in deduplication efficiency.
Memory usage per machine in SRB includes the Bloom filter space to access the on-disk index
and  cache for frequently or recently accessed chunk index.  
% SRB can deliver up to 97.935\% deduplication efficiency which is slightly better than VC.
% Thus this represents a tradeoff: VC provides better fault tolerance and fast
% approximate deletion with competitive (but slightly lower) deduplication
% efficiency.
% >>>>>>> 4dcd68612b052c0f890ed30361a9ed03771b5df1
%its loss of efficiency is caused by the routing of data chunks which restricts the search scope
%of duplicate detection.
%SRB provides slightly better deduplication efficiency than our VC approach, which we accept
%because we are rewarded by architecture-wise benefits such as fault-tolerance and fast 
%Though not our primary goal, this result does show that VC can remove competitive amount of duplicates.

@@

In summary, our experiments show that
version detection at the segment level can reduce the data size to about 24.14\% of original data, 
which leads to about a 75.86\% reduction. Namely 10TB snapshot data per machine is reduced to 2.414TB.
Similarity-guided local search can further reduce the data size
to about 1.205T, which is  12.05\% of original. Thus it delivers a 50.08\% reduction after the version-based
 deduplication.
The popularity-guided global deduplication with $\sigma=2\% $
reduces the data further to 860GB, namely 8.6\% of the original size. 
So it provides additional 28.63\% reduction.

The overall memory usage of VC for each physical machine is very small, which is insignificant to other 
hosted cloud services.  In comparison, the 2.4GB per-machine memory usage of SRB is very visible 
to other services.
% even each physical machine in the production environment has 48GB memory.

@@

Comparing the experiment results of the sampled index method reported in~\cite{Guo2011}, 
our scheme achives a 85K:1 ratio between raw snapshot data and memory usage 
with 96\% deduplication efficiency
while the sampled index method achives 20K:1 (10GB memory per 500TB raw data)
with 97\% deduplication efficiency.
Thus our scheme is more memory efficient with a good tradeoff for deduplication efficiency.
If we change $\sigma=4\%$, the deduplication efficiency of VC increases to 96.58\% while
memory usage per machine increses to about 220MB. 
Notice that the sampled index method is designed for single-machine deduplication
and it is not easy to extend to a distributed cluster architecture.

@@

Table ~\ref{tab:resource_usage} shows that when  each machine conducts
backup one VM at a time, the backup of the entire
VM cluster completes in about 1.31 hours. Since there are about 25 VMs per machine, we could execute
more tasks in parallel at each machine. But adding more backup concurrency does 
not shorten the overall time
significantly in this case because of the controlled  disk read bandwidth usage.
When I/O throttling is not used, we will show later that processing multiple VMs concurrently 
does improve the throughput of backup.
%,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
%at 40GB size, our snapshot system can finish backing up all the VMs (1TB total) in 1.58 hours.

@@

{\bf Throughput of software layers without I/O throttling.}
Table~\ref{tab:throughput} shows the  average throughput of software layers
when I/O throttling is not applied to control usage. The
%machine when all machine nodes execute one or multiple MV backup tasks.
``Backup'' column is the throughput  of the backup service  per machine.
``Snapshot store" is the  write throughput of the snapshot store layer and the significant reduction from this
column to  ``Backup" column is caused by deduplication.
Only non-duplicate chunks trigger a snapshot store write.
Column ``QFS'' is the write request traffic to the underlying file system after compression.
For example, with 148 MB/s write traffic to the snapshot store, QFS write traffic is about 35.3 MB/s
after compression.  However, the underlying disk storage traffic will be three times greater with replication.
The result shows that the backup service can deliver up to 5.46 GB/s 
per machine without I/O restriction
under 6 concurrent backup tasks. 
For our dataset, each version of total snapshots has abut 1TB per machine for 25 VMs and  thus  each machine
would complete the backup in about 3.05 minutes.
With a higher disk storage bandwidth available, the above backup
throughput would be higher. 
In comparison, the sampled index method in~\cite{Guo2011} achives about 5.5GB per second
with 16 concurrent backup tasks and 6GB per second with
more tasks.  The per-machine throughput of our scheme is reasonable.
%With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine in less than 1.31 hours.

>>>>

\section{Evaluation}
\label{sect:evaluation}
We have implemented and evaluated a prototype of our VC scheme on a Linux cluster of machines with
8-core 3.1Ghz AMD FX-8120 and 16 GB RAM. 
Our implementation is based on the Alibaba cloud platform~\cite{Aliyun,WeiZhangIEEE}
and the underlying DFS uses  QFS with default replication degree 3 while the PDS replication degree is 6.
Our evaluation objective is to
study deduplication efficiency and resource usage of VC,  
and assess its processing time and backup throughput, and  
the benefit in fault tolerance. 
We will compare VC with a VO approach  using stateless routing with binning (SRB) 
based on~\cite{Dong2011,extreme_binning09}.
SRB executes distributed deduplication by routing data chunks to cluster machines~\cite{Dong2011}
using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to
a machine, the chunk is compared with the fingerprint index within this machine locally based 
on~\cite{extreme_binning09}.

@@

Table~\ref{tab:efficiency-comparison} shows the deduplication efficiency and per-machine memory usage for SRB and VC with different 
settings.
% <<<<<<< HEAD
% Our deduplication efficiency is defined as the percent of duplicate chunks
% which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
% The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
% is defined in Table~\ref{tab:symbol}. 
% =======
Deduplication efficiency is defined as the percent of duplicate chunks which are removed
compared to a perfect scheme which detects and removes  all duplicates. 
% so only global perfect deduplication can have 100\% efficiency.
% We also compare several PDS sizes chosen for VC.
%(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
Notice $\sigma$ is the percentage of unique chunks selected in PDS.
With $\sigma =2\%$, Column 3 shows its 
%memory usage for PDS index lookup per machine is about 100MB per machine and  the 
deduplication efficiency can 
reach over 96\%. 
%When $\sigma=4\%$, Column 4 shows that the deduplication efficiency can reach 96.6\% while 
%more index space is allocated  per machine for  PDS fingerprint lookup.
The loss of efficiency in VC is caused by the restriction of the physical memory available
in the cluster for fast in-memory PDS index lookup. 
Memory usage per machine is low because each machine only hosts $1/p$  of  index for PDS 
plus some buffer space where $p$ is the number of physical machines. 
%In the extreme case if we put all the fingerprint into PDS 
%index ($\sigma=100\%$) then VC will have 100\% efficiency.
SRB in Column 5 can deliver up to 97.86\% deduplication efficiency, which is slightly better than VC.
Thus this represents a tradeoff as VC uses much less resource  and faster deletion.
%with a slight reduction in deduplication efficiency.
Memory usage per machine in SRB includes the Bloom filter space to access the on-disk index
and  cache for frequently or recently accessed chunk index.  
% SRB can deliver up to 97.935\% deduplication efficiency which is slightly better than VC.
% Thus this represents a tradeoff: VC provides better fault tolerance and fast
% approximate deletion with competitive (but slightly lower) deduplication
% efficiency.
% >>>>>>> 4dcd68612b052c0f890ed30361a9ed03771b5df1
%its loss of efficiency is caused by the routing of data chunks which restricts the search scope
%of duplicate detection.
%SRB provides slightly better deduplication efficiency than our VC approach, which we accept
%because we are rewarded by architecture-wise benefits such as fault-tolerance and fast 
%Though not our primary goal, this result does show that VC can remove competitive amount of duplicates.

@@

In summary, our experiments show that
version detection at the segment level can reduce the data size to about 24.14\% of original data, 
which leads to about a 75.86\% reduction. Namely 10TB snapshot data per machine is reduced to 2.414TB.
Similarity-guided local search can further reduce the data size
to about 1.205T, which is  12.05\% of original. Thus it delivers a 50.08\% reduction after the version-based
 deduplication.
The popularity-guided global deduplication with $\sigma=2\% $
reduces the data further to 860GB, namely 8.6\% of the original size. 
So it provides additional 28.63\% reduction. 
The overall memory usage of VC for each physical machine is very small, which is insignificant to other 
hosted cloud services.  In comparison, the 2.4GB per-machine memory usage of SRB is very visible 
to other services.
% even each physical machine in the production environment has 48GB memory.

@@

Comparing the experiment results of the sampled index method reported in~\cite{Guo2011}, 
our scheme achives a 85K:1 ratio between raw snapshot data and memory usage 
with 96\% deduplication efficiency
while the sampled index method achives 20K:1 (10GB memory per 500TB raw data)
with 97\% deduplication efficiency.
Thus our scheme is more memory efficient with a good tradeoff for deduplication efficiency.
If we change $\sigma=4\%$, the deduplication efficiency of VC increases to 96.58\% while
memory usage per machine increses to about 220MB. 
Notice that the sampled index method is designed for single-machine deduplication.
%and it is not easy to extend to a distributed cluster architecture.

@@

Table ~\ref{tab:resource_usage} shows that when  each machine conducts
backup one VM at a time, the backup of the entire
VM cluster completes in about 1.31 hours. Since there are about 25 VMs per machine, we could execute
more tasks in parallel at each machine. But adding more backup concurrency does 
not shorten the overall time
significantly in this case because of the controlled  disk read bandwidth usage.
When I/O throttling is not used, we will show below that processing multiple VMs concurrently 
does improve the throughput of backup.
%,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
%at 40GB size, our snapshot system can finish backing up all the VMs (1TB total) in 1.58 hours.

@@

{\bf Throughput of software layers without I/O throttling.}
Table~\ref{tab:throughput} shows the  average throughput of software layers
when I/O throttling is not applied to control usage. The
%machine when all machine nodes execute one or multiple MV backup tasks.
``Backup'' column is the throughput  of the backup service  per machine.
``Snapshot store" is the  write throughput of the snapshot store layer and the significant reduction from this
column to  ``Backup" column is caused by deduplication.
Only non-duplicate chunks trigger a snapshot store write.
Column ``QFS'' is the write request traffic to the underlying file system after compression.
For example, with 148 MB/s write traffic to the snapshot store, QFS write traffic is about 35.3 MB/s
after compression.  However, the underlying disk storage traffic will be three times greater with replication.
The result shows that the backup service can deliver up to 5.46 GB/s 
per machine without I/O restriction
under 6 concurrent backup tasks. 
For our dataset, each version of total snapshots has abut 1TB per machine for 25 VMs and  thus  each machine
would complete the backup in about 3.05 minutes.
With a higher disk storage bandwidth available, the above backup
throughput would be higher. 
In comparison, the sampled index method in~\cite{Guo2011} achives about 5.5GB per second
with 16 concurrent backup tasks and 6GB per second with
more tasks.  Thus the per-machine throughput of our scheme is reasonable.
%With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine in less than 1.31 hours.
